\documentclass[9pt,a4paper]{altacv}

% \usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}
% \usepackage[]{biblatex}
\usepackage[default]{lato}
% \usepackage{hyperref}


\begin{document}

% Change the colours:
\definecolor{onyx}{rgb}{0.06, 0.06, 0.06}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{onyx}
\colorlet{accent}{onyx}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{SlateGrey}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% sample.bib contains your publications
% \addbibresource{sample.bib}



\name{CHACKO BABU}
\tagline{Data Analyst with close to 8 years' experience working with data in diverse domains; corporate, academia, NGO and freelancing. Possesses demonstrable skills in areas of data sourcing, tidying and exploring, conducting statistical analyses and communication of results. Driven to leverage my expertise in statistical techniques and programming skills to solve business problems and enhance team capabilities.}
\personalinfo{
  \email{\href{chackobabun@gmail.com}{chackobabun@gmail.com}}
  \homepage{\href{https://chackobabu.github.io/}{ chackobabu.github.io}}
  % \linkedin{\href{https://www.linkedin.com/in/chacko-babu-29834214b/}{linkedin.com/in/chacko-babu-29834214b}}
  \location{Bengaluru, Karnataka}
  \phone{+918086249788}
 }


%% Make the header extend all the way to the right, if you want.
% \begin{fullwidth}
\makecvheader
% \end{fullwidth}

% \begin{fullwidth}

% \begin{center}
\cvsection{Professional Experience}

\cvemployer{Euromonitor International}{Bengaluru, Karnataka}
\cvrole{Data Analyst}{February 2024 - present}
\begin{itemize}
    \item Developed a web-based application to extract data from an internal database. The application features an interface that allows users to select multiple parameters to define the required information. The connected server extracts data from various API endpoints and transforms it into downloadable data frames. This process significantly improved data accessibility of the team, saved labor hours, and eased project timelines.
    \item Designed and implemented a user-friendly program enabling seamless editing of the internal database through API calls, enhancing data management efficiency and user experience.
    \item Conducted bite-sized training sessions to familiarize colleagues with the scripts, enhancing their understanding and usage of the tools.
    \item Developed several scripts to efficiently scrape data from retailer websites and transform it into structured data frames. Additionally, created scripts to parse information from PDF files, utilizing the effectiveness of regular expressions.
    \item Designed and executed statistical models to forecast market sizes and project market share growth. Additionally, I have led training sessions for colleagues on topics such as outlier detection techniques, as well as foundational principles of descriptive and inferential statistics.
    \item Proficiently utilized SQL commands to extract data from BigQuery and MySQL tables, enabling efficient data retrieval for analysis and insights.
    \item Leveraged the Linux CLI to administer tasks and operations on a virtual machine hosted within the Azure cloud environment.
\end{itemize}

\cvrole{Research Associate}{April 2022 - January 2024}
\begin{itemize}
    \item Designed and implemented a system to automate the creation of Excel files, generating market-specific files at the onset of research and consolidating them afterward into a master file for analysis purposes. This streamlined process led to a substantial enhancement in data accuracy and a notable reduction in labor hours.
    \item Performed thorough desk researches for in-depth market analysis.
    \item Crafted dynamic Tableau dashboards to visually illustrate evolving industry trends.
    \item Proactively addressed ad-hoc requests for programming solutions and conducted descriptive statistical analyses and visualisations for various teams across the organization.
\end{itemize}
\divider
\cvemployer{Mizuho India Japan Study Center, IIM-Bangalore}{Bengaluru, Karnataka}
\cvrole{Research Associate}{November 2021 - March 2022}
\begin{itemize}
    \item Analysed data from factories’ production floors for metrics such as line-efficiency, synchronization ratio etc, to identify areas for improvement.
    \item Contributed to a team effort to develop a ranking index for small manufacturing enterprises and startups, utilizing a range of selected parameters. The objective was to facilitate connections between enterprises seeking investment and Japanese investors.
\end{itemize}
\divider
\cvemployer{Dept. of Economics and Social Sciences, IIM-Bangalore}{Bengaluru, Karnataka}
\cvrole{Academic Associate}{August 2018 - July 2021}
\begin{itemize}
    \item Contributed significantly in various empirical research projects in fields of international trade, migration, behavioural economics, financial economics etc.
    \item Extracted data from various public sources to build models and test various hypotheses using statistical and econometric methods.
    \item Worked as a Teaching Assistant which involved routinely taking tutorials for management students, associating closely with professors in research for course material, and coordinating class room activities in general; major courses handled were Advanced Microeconomics, Advanced Macroeconomics, Financial Economics.
\end{itemize}
\newpage
\cvemployer{Centre for Development Studies}{Thiruvananthapuram, Kerala}
\cvrole{Research Assistant}{July 2017 - March 2018}
\begin{itemize}
    \item Worked with multiple rounds of large-scale datasets of National Sample Survey for the study, along with other datasets such as KLEMS by RBI for various research projects.
    \item Contributed to a project by tidying up large volumes of primary survey data, and making it analysis ready.
\end{itemize}

\cvsection{Freelance Projects / Consulting Engagements}
\cvemployer{India Migration Now}{Remote}
\cvrole{Data Analyst (Freelance)}{September - December 2021}
\begin{itemize}
    \item Analyzed data from KoboToolBox on the NGO's daily operations and regularly updated a Tableau dashboard to visualize trends, enabling data-driven decision-making.
    \item Proactively addressed ad-hoc requests for data-wrangling and visualisations for reports and newsletters.
\end{itemize}
\divider
\cvemployer{National Law School India University}{Bangalore, Karnataka}
\cvrole{Data Analysis Project}{October 2021}
\begin{itemize}
    \item Analysed results of a primary survey done among migrant construction labourers in Bangalore to probe the question of efficacy of government welfare schemes.
\end{itemize}
\divider
\cvemployer{NSRCEL, IIM-Bangalore}{Bangalore, Karnataka}
\cvrole{Data Science Project}{August - September 2021}
\begin{itemize}
    \item Analysed results of a primary survey on women entrepreneurs (participants of Goldman Sachs 10k Women program) for challenges they face in their entrepreneurship journey. Performed NLP techniques (specifically sentence clustering and sentiment analysis) on the data. 
    \item Communicated the results of the analysis with actionable insights using visualisations and tables to stakeholders.
\end{itemize}
\divider


\cvsection{Education}
\cvemployer{Madras Christian College}{Chennai, Tamil Nadu}
\cvrole{MA Economics}{2013 - 2015}
\begin{itemize}
    \item \textit{Dissertation:} Analysis of the socio-economic profiles of migrant labourers in seafood processing firms in Alappuzha, Kerala; data was collected personally using a primary survey of a total 70 of laborers from seven seafood processing units.
    \item Held the position of convenor of annual inter-collegiate economics fest, "Artha" in my second year.
\end{itemize}
\divider
\cvemployer{St Joseph’s College of Arts and Science}{Bangalore, Karnataka}
\cvrole{BA Economics}{2010 - 2013}
\begin{itemize}
    \item \textit{Dissertation:} Critical analysis of ’Kerala Model of Development’ and its contemporary relevance.
\end{itemize}


% \end{fullwidth}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.



\end{document}
